Synpotic Soil Characterization

### 2024-07-30 3-reports/manuscript_figures.Rmd
renaming bc f-ing sync issues
analytes figures

```{r analytes, fig.height = 4, fig.width = 4}

@@

>>>>

Version 1 - one region only

```{r analytesx, fig.height = 4, fig.width = 4}

@@

Version 2 - both regions

```{r analytesx-2, fig.height = 4, fig.width = 8}
data_combined_wide %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = Fe))+
  geom_violin(aes(fill = transect), alpha = 0.4)+
  geom_jitter(width = 0.1)+
  labs(x = "",
       y = "Extractable Fe, μg/g")+
  facet_wrap(~region)+
  scale_fill_manual(values = pal_transect)+
  theme(legend.position = "none")

data_combined_wide %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = P))+
  geom_violin(aes(fill = transect), alpha = 0.4)+
  geom_jitter(width = 0.1)+
  labs(x = "",
       y = "Extractable P, μg/g")+
  facet_wrap(~region)+
  scale_fill_manual(values = pal_transect)+
  theme(legend.position = "none")
```
